---
title: "GSOC Glyph Maps Tests"
format: pdf
editor: visual
editor_options: 
  chunk_output_type: console
---

## Test 1 (Easy):

Download the `cubble` package and run the glyph map examples (`?geom_glyph`).

```{r}
#| label: load-pkg-data
#| warning: false
#| message: false

if (!require("cubble")) {
  install.packages("cubble")
  library(cubble)
}
library(tidyverse)
```

```{r}
#| label: ggally-example-basic
#| message: false

# basic glyph map with reference line and box---------------
p <- ggplot(data = GGally::nasa,
       aes(x_major = long, x_minor = day,
           y_major = lat, y_minor = surftemp)) +
  geom_glyph_box() +
  geom_glyph_line() +
  geom_glyph() +
  theme_bw()
p
```

```{r}
#| label: glyph-example-rescaled

# rescale on each individual glyph ---------------
p <- ggplot(data = GGally::nasa,
       aes(x_major = long, x_minor = day,
           y_major = lat, y_minor = surftemp)) +
  geom_glyph(global_rescale = FALSE)
p
```

```{r}
#| label: glyph-example-adjusted

# adjust width and height with relative & absolute value ---------------
p <- ggplot() +
  geom_glyph(data = GGally::nasa,
             aes(x_major = long, x_minor = day,
                 y_major = lat, y_minor = surftemp),
                 width = rel(0.8), height = 1) +
   theme_bw()
p
```

```{r}
#| label: glyph-example-polar

# apply a re-scaling on Y and use polar coordinate
p <-
  GGally::nasa %>%
  ggplot(aes(x_major = long, x_minor = day,
             y_major = lat, y_minor = ozone)) +
    geom_glyph_box(fill=NA) +
    geom_glyph_line() +
    geom_glyph(y_scale = GGally::range01, polar = TRUE)
p
```

\pagebreak

## Test 2 (Medium):

read [the `Geoms` section](https://ggplot2.tidyverse.org/reference/index.html#geoms) in the ggplot2 package reference and other geoms available in the ggplot2 extensions. Create a example that is applicable to be used as a glyph on a map.

I think all of the following geoms can be appropriately used as glyphs in order to visualize spatio-temporal data.

```{r}
#| label: glyph-examples
#| message: false
#| warning: false

library(palmerpenguins)
library(ggridges)
# install.packages("ggridges")

penguins_grouped <- penguins |>
  group_by(year) |>
  summarise(
    mean_bill = mean(bill_length_mm, na.rm = TRUE), 
    mean_mass = mean(body_mass_g, na.rm = TRUE)
  )

# Density Plots
ggplot(penguins) +
  geom_density(aes(x = bill_length_mm, group = year, color = factor(year)), show.legend = FALSE) +
  theme_void()

# 2d Density Plots
ggplot(penguins) +
  geom_density_2d(aes(x = bill_length_mm, y = body_mass_g), show.legend = FALSE) +
  theme_void()

# Ridgeline plots
ggplot(penguins) + 
  geom_density_ridges(aes(x = year, y = sex, fill = sex), show.legend = FALSE) + 
  theme_void()

# Bar Charts
ggplot(penguins) +
  geom_bar(aes(x = year, fill = factor(year), group = year), show.legend = FALSE) +
  theme_void()
```

\pagebreak

## Test 3 (Hard):

See <https://github.com/huizezhang-sherry/cubble/pull/28>
